Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
recorder casts

\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}

@@

\newcommand{\cOOcast}[3]{#1 \overset{#2}{\Rightarrow} #3}
\newcommand{\vOOcast}[2]{#1\langle#2\rangle}

@@

\todo[inline]{Please fill in the missing reduction rules. -JS}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
        It's better because it matches the postfix syntax we are using for
        casts. Currently line 2 of applyCast for D is difficult to read,
        compare it with line 4 of applyCast for UD. -JS
        }

>>>>

\newcommand{\eOOcast}[4]{\langle \cOOcast{#2}{#3}{#4} \rangle #1}

@@

%\newcommand{\cOOcast}[3]{#3 \overset{#2}{\Leftarrow} #1}
\newcommand{\cOOcast}[3]{#3 \Leftarrow^{#2} #1}
\newcommand{\vOOcast}[2]{\langle#2\rangle#1}

@@

\todo[inline]{Please fill in the missing reduction rules. -JS}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    }
